\documentclass[margin,line, 11pt, a4paper]{res}

\usepackage {fullpage}
%\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\voffset = -0.5 in
\oddsidemargin -0.5in
\evensidemargin -0.5in
\headheight= -1.5pt
\topmargin = -0.5pt
\textwidth=5.8in
\textheight = 780pt
\itemsep=0in
\parskip=0.04in
\parsep=0in


\newenvironment{list1}{
  \begin{list}{}{%
      \setlength{\itemsep}{.1in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{.07in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{.02in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{.05in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}
\pagestyle{empty}
\name{ {\Large Chi-Wei Tseng} \hspace*{2.53in} {\small Computer Science MS Program Applicant} \vspace*{0.1in}}

%\begin{flushleft}
%  {\bf \large Yu-Hsien Hwang Fu} \hfill {\bf \small Chemistry and Chemical Biology Ph.~D.~Program Applicant}  \hfill \vspace*{1in}
%  \HRule
% \end{flushleft}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{p{3.3in}p{2.1in}}
79 Wen-Hua Road & {\it Phone:} 886-2-29250988\\
Yong-He District & {\it Mobile:} 886-982-017156\\
New Taipei City, Taiwan & {\it E-mail:} kiwaygo@gmail.com\\
\end{tabular}

%
%\section{\sc Research Interests}
%Bayesian statistics, spatial statistics, nonparametric regression,
%statistical methods for large datasets, statistics for public policy

\section{\sc Education}
{\bf National Taiwan University}, Taipei, Taiwan

\begin{list1}
\item B.S.~in Computer Science \& Information Engineering \hfill {\bf Sep.~2008 -- Jun.~2012}

\begin{list2}
{\small \item Major GPA: 3.86/4.0
\item Undergraduate Research Project: ``Lighting-By-Guide System''\\Advisor: Prof.~Yung-Yu Chuang}
\end{list2}

\item B.S.~in Chemistry \hfill {\bf Sep.~2007 -- Jun.~2012}

\begin{list2}
{\small \item Major GPA: 3.58/4.0
\item Bachelor Thesis: ``Electronic Coherence Two-Dimensional Spectroscopy''\\Advisor: Prof.~Yuan-Chung Cheng}
\end{list2}
\end{list1}
{\bf Taipei Municipal Jianguo (Chien-Kuo) High School}, Taipei, Taiwan
\begin{list1}
\item High School Diploma \hfill {\bf Sep.~2004 -- Jun.~2007}
\end{list1}

\section{\sc Honors and Awards} 
{\bf Poster Award for the Excellence of Undergraduate Research}, Dept.~of Chemistry, National Taiwan University, 2011

\section{\sc Research Experience}

{\bf Communications and Multimedia Lab}, National Taiwan University

\item{\em Undergraduate Student} \hfill {\bf Aug.~2011 -- Jun.~2012}

{\small We focused on alleviating workloads of lighting artists in 3D computer animation production through developing an efficient, effective and automatic algorithm which approximates the lighting configuration in a scene from an artistic illustration of the anticipated render. Advised by Prof.~Yung-Yu Chuang.}

\vspace{.1in}
{\bf Theoretical Chemistry Lab}, National Taiwan University

\item {\em Undergraduate Student} \hfill {\bf Aug.~2010 -- Jun.~2012}

{\small We aim at redesigning 2D electronic spectroscopy to probe electronic coherences and correlations in energy gap fluctuations. A time-nonlocal quantum master equation approch is applied to simulate and verify the feasibility of the proposition. Advised by Prof.~Yuan-Chung Cheng.}

\section{\sc Selected Courses}
\begin{tabular}{p{2.5in}p{2.5in}}
 Digital Image Synthesis (95) & Interactive Computer Graphics (95)\\
 Digital Visual Effects (90) & GPU Programming (A+) \\
 Digital Image Processing (A) & Computational Photography (A)
\end{tabular}

\section{\sc Selected Projects}
{\bf Super-Resolution Video Player} \hfill {\bf Apr.~2012 -- Jun.~2012}

{\small a GPU-based video player which enhances resolution with Freeman and Fattal's ``upscaling from local self-examples'' on playing}

{\bf Milktea Rendering} \hfill {\bf Dec.~2010 -- Jan.~2011}

{\small a simulator which combines Jos Stam's ``stable fluid'' and marching cubes algorithm to render the procedure of pouring milk into a swirling glass of black tea}

{\bf Raybomb Raytracer} \hfill {\bf Dec.~2009 -- Feb.~2010}

{\small a renderer accelerated with Intel's streaming SIMD extensions}

\section{\sc Participated Activities}
{\small
Member of Digital Movie Creators' Club, Natl. Taiwan Univ. \hfill Sep.~2010 -- Jun.~2011

Director, Senior Musical for Dept.~of Chem. \hfill Jan.~2011 -- Apr.~2011

Co-Director of Graphic Arts, Student Association, Dept.~of Chem. \hfill Sep.~2009 -- Jun.~2010

Member of Table Tennis Team, Dept.~of Chem. \hfill Sep.~2007 -- Jun.~2010

}
\end{resume}
\end{document}
